\documentclass[chi_draft]{sigchi}


\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix,endnotes}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}

\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

% \bibliographystyle{SIGCHI-Reference-Format}
\renewcommand*{\notesname}{Graveyard of old paragraphs}
\makeatletter
\def\blx@maxline{77}
\makeatother


% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.

\newlist{inlinelist}{enumerate*}{1}
\setlist*[inlinelist,1]{%
  label=\arabic*),
}

\setlist{nolistsep}
\def\plaintitle{Reexamining Crowd Work: A Historical Framing of On--Demand Labor as Piecework}
\def\plainauthor{All the people (Ali, Margaret, MSB, who else?)}
\def\emptyauthor{}
\def\plainkeywords{Crowdsourcing}
\def\plaingeneralterms{Documentation, Standardization}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{
    \def\UrlFont{\sf}
  }{
    \def\UrlFont{\small\bf\ttfamily}
  }}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\definecolor{BrickRed}{HTML}{FF0000}
\definecolor{JokeGreen}{HTML}{00C953}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{BrickRed}[al2: #1]}}

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}
\bibliography{references}
% \addbibresource{references}

\newcommand{\subsubsubsection}[1]{\textit{#1}}

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\newcommand{\topic}[1]{\textbf{#1}} % if you're in a subfile, bold the \topic sentences to make it easier to skim/diagnose logical issues
\newcommand{\joke}[1]{{\color{JokeGreen}#1}} % if you're in a subfile, make the joke JokeGreen colored so people know I'm being funny!
\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}



\title{\plaintitle}

\numberofauthors{3}
\author{%
  \alignauthor{Leave Authors Anonymous\\
    \affaddr{for Submission}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
  \alignauthor{Leave Authors Anonymous\\
    \affaddr{for Submission}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
  \alignauthor{Leave Authors Anonymous\\
    \affaddr{for Submission}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
}

\maketitle
\begin{abstract}
  With growing attention toward on--demand labor
  --- ranging from the ``sharing economy'' to information work ---
  scholars have made connections to various frameworks 
  and mechanisms such as worker advocacy, empowerment, and Taylorism,
  to make sense of our observations of
  on--demand work and the workers that power this movement.
  We argue that the literature surrounding ``piecework''
  informs and even predicts both the contributions
  that have been made toward the development of on--demand labor and crowd work
  as well as the fallout among workers and researchers
  with regard to the disillusionment and alienation of work.
  
  After evaluating this framing
  through a series of case studies,
  we look to the future
  to identify worthwhile questions and
  points of inquiry, such as the movement toward factories,
  that researchers in social computing should consider
  as we attempt to anticipate and perhaps shape the future of work.
\end{abstract}

\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous} \category{See
  \url{http://acm.org/about/class/1998/} for the full list of ACM
  classifiers. This section is required.}{}{}

\keywords{\plainkeywords}
\subfile{introduction.tex}
\subfile{cases.tex}

\section{The Bleak Future of Crowd Work}
We've traced a path from piecework itself through
the processes that describe the design and implementation of piece work and crowd work as part of the same thread;
in tracing this process, we touched on the relationships between decomposition,
work \& worker abstraction,
flexibility, and followed through both the general fallout of crowd work in the research community
as well as the fallout between workers and the managers and other external parties
--- including researchers.

Throughout these case studies, we have pointed out the parallels between
the contemporary research in on--demand labor and
the much larger body of research constituting our understanding of topics such as
piecework, factory work, and laborer relations.
If we agree that this framing is useful and informative, then
several topics emerge as relatively open questions in the study of crowd work and on--demand labor.
Two of the most pressing questions are
\begin{inlinelist}
\item the beginnings of factories, and 
\item the decline of relevance of worker advocacy organizations.
\end{inlinelist}
We will discuss those questions here.



\subsection{The beginnings of factories}\label{sec:Factorization}
We established earlier that abstracted work and low wages tend to result in variable outcomes,
which presents problems for employers.
% So work output is variable, and that's bad. What are we doing about it?
Historically, this is what led to factories; by employing a cohort of known workers,
we can be reasonably assured that the quality of the work will be better than random.
Furthermore, we can invest more resources in training workers and
get workers to do more complex work with more context.
% you would pay some experts who understood what they needed to do
% and they would form a cohort into which you invest more.

Some research already looks at research such as investing in workers, and
informally, we know that this happens among industry requesters
\cite{jonBrelig,shepherdingDow}.
AMT, meanwhile, offers requesters the ability to create tasks which are
not just hidden from unqualified workers by default, but completely.
Requesters have taken to using lists of worker IDs which reference
workers who have proven their reliability,
representing a sort of proto--organization of loosely connected workers.

This, then, suggests that the beginning of the regularization of workforces
--- a sort of coalescence of factories ---
is already happening.
If our framing of on--demand labor is accurately describing an underlying relationship with piecework,
then we should watch for the emergence and popularization of persistent teams of workers.
% While this field site will likely prove exceedingly difficult to 
% Social computing researchers should seek to understand this process more
% fully, as we a

\subsection{The decline of advocacy organizations}
The rise of labor unions in the \nth{20} century seems to have been precipitated by
severely unjust conditions imposed on workers in factories and elsewhere
\cite{ebbinghaus1999institutions}.
Incidents broadly describing this dynamic can be found in research on AMT
\cite{turkopticon,dynamo}.
If these are prototypical labor advocacy organizations of contemporary on--demand work,
the next question we should look to is if
--- and indeed \textit{how} ---
these institutions might face challenges in the future.

For insight on this, we return to \citeyear{levi2009union}'s study of labor unions,
and identify that
``Scholars who evaluate union governance by procedural criteria generally find that oligarchy tends to arise and persist even when democratic procedures are in place''
\cite{levi2009union}.
Indeed, \citeauthor{levi2009union} writes about the general perception that labor unions were either
% unable to satisfy their needs or otherwise more invested in the 
This perception already appears to be emerging in digitally mediated peer--governed organizations,
as \citeauthor{keegan2010egalitarians} and others have illustratively documented
\cite{beschastnikh2008wikipedian,keegan2010egalitarians}.
If these organizations and others are to avoid the same fate that labor unions faced,
they should take care to study this phenomenon and attempt to avoid it.

\section{Implications for Design}
If it's agreed that
the major topics we've discussed thus far are related and
--- at least to \textit{some} extent ---
precipitated in the fashion we argue,
then we have a rare opportunity as researchers,
and as agents of change in the communities we study,
to affect change on the dynamics of crowd and on--demand work
as they continue to develop.

Without claiming to have easy, cut--and--dry solutions to these problems,
we can nevertheless bring to attention a number of critical opportunities to
learn from historical parallels in piecework and factory labor,
and make informed decisions regarding whether
(or indeed how)
we may want to influence outcomes.
The challenges we bring to attention here are as follows:
\begin{inlinelist}
  \item codifying investment toward collective goods into the designs of systems;
  \item (re--)decentralizing the internet; and
  \item enabling reputation transferral.
\end{inlinelist}


\subsection{Codify the common good}
As \citeauthor{lessig2006code} points out in his book,
digital media give designers the opportunity to design and build into the systems
policies and practices to contribute to the collective benefit of the people therein
\cite{lessig2006code}.
Historically, the confluence of forces \citeauthor{lessig2006code} describes
would ultimately result in outcomes such as benefits for workers,
funds for sick leave and vacation, and other conveniences.
The transient nature of on--demand work would seem to problematize this arrangement,
but we can discuss and explore the viability of building into systems the mechanisms necessary
to save a portion of payment from every gig,
record taxable income, or
myriad other generally administrative tasks automatically.


\subsection{Decentralize the internet --- again}
Digitally mediated on--demand labor markets have historically been insular and incompatible with one another,
forcing workers either to choose one or juggle participation in these markets with great difficulty.
An ``API'' for on--demand labor markets could make it possible for any person
or organization to instantiate their own marketplace and inter--operate with.
This can be changed, and indeed must, if we are to realize the hopes of early researchers who advocated the
democratizing nature and power of the internet
\cite{barlow2009declaration,lanier2014owns}.

\subsection{Deal with reputation}
Reputation systems in on--demand labor markets are fundamentally broken.
To say nothing of the fact that information workers (such as those on AMT) can't transfer their reputations to qualitatively different forms of labor
like driving--for--hire (e.g. Uber), even within the same industry
it's currently not feasible for workers to transfer their reputations or other information from one place to another.
This affects more than the reputation and trustworthiness of workers;
accounting for things such as taxes, benefits, etc\dots is all but left to the individual workers, who struggle with myriad bureaucratic obstacles.
We can design systems that facilitate the aggregation and, more importantly, the transferral of reputation, income, and other features of work.



\section{Discussion}
We've discussed a number of aspects of on--demand work that
offer parallels with historical piecework.
Perhaps more importantly, we've hopefully demonstrated that the dynamics we observe in on--demand work
are interrelated and follow from one another just as necessarily as they did in
the development and maturation of piecework and factory work through the \nth{20} century.
This framing on on--demand work should, we hope, provide us with the necessary historical context
to make better--informed design decisions about how we want ``the future of crowd work'' to look.

\section{Conclusion}
\citeauthor{crowdworkFuture} discussed many of the challenges and problems in crowd work in \citeyear{crowdworkFuture},
but didn't necessarily situate the notion of crowd work in a broader context.
This paper attempts to fill that gap, and in doing so hopes
to give the research community theoretical grounding to work with and within on--demand labor more successfully.
But more than that, we hope to have addressed important questions to inform how we actually might make crowd work
a career in which we want our children to work.


\balance{}
\printbibliography


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
