\documentclass[11pt]{article}
\usepackage{balance,graphics,times,setspace}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue,anchorcolor=blue]{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage[inline]{enumitem}
\usepackage[tiny,compact]{titlesec}

% \hypersetup{ colorlinks=true,linkcolor=blue}
% \setlength{\parskip}{.4em}

\setlist[itemize]{itemsep=0pt,topsep=0pt,parsep=0pt}
\setenumerate{itemsep=0pt,topsep=0pt,parsep=0pt}
\def\labelitemi{--}

% \newlist{inlinelist}{enumerate*}{1}
% \setlist*[inlinelist,1]{%
%   label=\arabic*),
% }



\begin{document}
  \begin{center}
  \Large{\textbf{Timeline}}
  \end{center}
  % \textit{A person's community of origin is an irrelevant factor in emerging modes of digitally enabled labor.}

% \begin{enumerate}[label=Week \arabic*:]
\section*{November: The Forum}
  \begin{itemize}
    \item Recruiting interested workers (10--20 people)

    \textit{We don't need to be ``Internet--scale'' right off the bat; the big challenge will be figuring out how to make interactions work in a digital medium; we'll tackle the ``interactions at scale'' issue later.}
    \item Hashing out norms ---
    bylaws, policies, etc\dots
    \item Figuring out system specifications ---
    Defining how an automatic system should behave \& what interactions it should make available
    (e.g. how much information customers should be able to see)

    \textit{Much of this has been worked out with Casa Latina, but I think it's important that every work group arrives at a conclusion about this sort of stuff actively, rather than have it put upon them.}
    \item Start narrowing down a developer.

    \textit{Finding a good developer will be absolutely crucial.
    I (Ali) still want to be very involved so if something happens to the site/platform I have a vague sense of how to fix it,
    but this person should be primarily committed to the project.
    We can work out how that will generally work in detail after we've narrowed our candidates list.}
  \end{itemize}
\section*{December: Prototype}
  \begin{itemize}
    \item Immediately: Ali making it work via ``\href{https://en.wikipedia.org/wiki/Wizard_of_Oz_experiment}{Wizard of Oz}''

    \textit{This is part of why we don't want lots of workers --- so that I can handle the amount of work figuring out work assignments and whatnot. It'll also inform whichever person is building the system.}
  \end{itemize}
\section*{December--January: Software}
  \begin{itemize}
    \item Hire a developer, make code open--source for collaborators.

    \textit{As before, this developer will be implementing major components of the platform, although the code itself should remain open--source, especially if we hope to encourage contributors to participate.}
    \item Essentially, start working on software to replace all of the things Ali's doing in the prototype run.
  \end{itemize}
\section*{January: Ramp--up}
  \begin{itemize}
    \item At this point we should be transitioning to the automated/software system,
    so Ali won't be doing dispatch anymore.
    
    \textit{
      This is where we'll identify issues that maybe Ali was intuitively working around without documenting,
      or handling any bugs or issues that might cause problems for workers absent a human handling dispatch.}
  \end{itemize}
\section*{February--April: 3--month run}
  \begin{itemize}
    \item Handling everything via the software--based system (i.e. Ali won't be running dispatch, making reviews work, etc\dots)

    \textit{The goal of this 3--month phase is to establish a running track of the cooperative working (both in the sense of getting work done and functioning properly).}
  \end{itemize}
\section*{May: Write}
  \begin{itemize}
    \item I'll want to write about the findings of this
    (hopefully) successfully--running cooperative work group.
    With the deadline for \href{http://cscw.acm.org/2016/index.php}{Computer--Supported Cooperative--Work}
    (A Human--Computer Interaction conference) in late May,
    I'll want to have ample time to write up my notes.
  \end{itemize}
\section*{Later: Scale}
  \begin{itemize}
    \item First to around 50 workers, then to around 100, then to around 150 or 200.
    \item \textit{Each milestone represents a different \textbf{kind} of group --- a group of 10 operates differently from a group of 50; a 50--person group operates differently from a 100--person group; etc\dots}
  \end{itemize}

% \end{enumerate}
% \bibliographystyle{acm}
% \bibliography{../references.bib}
\end{document}